---
title: "simpleRegress"
author: "Sabrina Andres"
date: "Summer 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```
## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).

I will try to model the length of the bear by its chest size.

## Model LENGTH ~ CHEST  

```{r}
my_chest <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(my_chest)
summary.lm(my_chest)
```

In the first model, the Residual Standard error was 5.37 and the Adjusted R-squared was 0.747, when comparing the length of the bear to its neck. However, in the second model, the Residual Standard Error decreased to 4.93 and the Adjusted R-squared increased to 0.786. The two models show the Adjusted R-square has increased with the second model. Meanwhile the Residual Standard Error has decreased with the second model, when comparing the length of the bear to its chest. The first(SIMP) model, was used in the first graph to compare the length~neck and the second(my_chest) model was used to compare the length~chest.

## Model LENGTH ~ AGE  

```{r}
my_ages <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE,data=bears)
abline(my_ages)
summary.lm(my_ages)
```

The my_ages model shows the Adjusted R_squared 0.507 and the Residual Standard Error 7.51. Which means just as one value increased so did the other.

## Model LENGTH ~ WEIGHT  this is an example  

```{r}
my_weight <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(my_weight)
summary.lm(my_weight)
```

The my_weight model shows Residual Standard Error is 5.43 and the Adjusted R-squared is 0.742. That means the Residual Standard Error has increased, while, the Adjusted R-squared decreases.

## Model LENGTH ~ HEADLEN

```{r}
headlen <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(headlen)
summary.lm(headlen)
```

While the residual standard error is 4.23, the adjusted R-squared is 0.843. This means the residual has dropped at least 1.0 from the original table. Meanwhile, the has increased. So far, it is the best model.


